Inferential Analysis of the \\ Supreme Court Citation Network

### 2018-01-04 Tex/presentations/SPSA2018/DesmaraisSPSATalk.tex
added notation to daggish plot
finished daggish plot

@@

\includegraphics[width = 0.95\textwidth,trim= 0cm 0cm 0cm 1.5cm,clip=true  ]{../../../Tex/images/daggish.pdf}

@@

The probability  of observing the $N_t \times N_{\leq t}$ adjacency matrix $C_t$ is
\[
\mathcal{P}(C_t, \bt) = \frac{\exp \{ \bt' \bh(C_{\leq t})  \}}{\sum_{C^*_t \in \mathcal{C}_t} \exp \{\bt ' \bh(C^*_{\leq t})\}  }
\]
Decomposition:
\[
\underbrace{\bh(C_{\leq t})}_{Net\hspace{3pt} Stats} \qquad \underbrace{\bt}_{Effects} \qquad \underbrace{\exp \{\bt' \bh(C_{\leq t}) \}}_{+ \hspace{3pt} Weight} \qquad \underbrace{\sum_{C^*_t \in \mathcal{C}_t} \exp \{\bt ' \bh(C^*_{\leq t})\}}_{Normalizer}
\]

>>>>

The probability  of observing the $N_t \times N_{\leq t}$ adjacency matrix $C_t$ given past citations $C_{<t}$, where $C_{\leq t}$ is the network up to time $t$
\[
\mathcal{P}(C_t|C_{<t}, \bt) = \frac{\exp \{ \bt' \bh(C_{\leq t})  \}}{\sum_{C^*_t \in \mathcal{C}_t} \exp \{\bt ' \bh(C^*_{\leq t})\}  }
\]
Decomposition:
\[
\underbrace{\bh(C_{\leq t})}_{Net\hspace{3pt} Stats} \qquad \underbrace{\bt}_{Effects} \qquad \underbrace{\exp \{\bt' \bh(C_{\leq t}) \}}_{+ \hspace{3pt} Weight} \qquad \underbrace{\sum_{C^*_t \in \mathcal{C}_t} \exp \{\bt ' \bh(C^*_{\leq t})\}}_{Normalizer}
\]

@@

\includegraphics[width = 0.95\textwidth,trim= 0cm 0cm 0cm 0cm,clip=true  ]{../../../Tex/images/daggish.pdf}

@@
